Auditory Scene Similarity Retrieval and Classification with Relevance based Quantization of Scattering Features

### 2016-12-06 paper/responseToReviewers.tex

\documentclass[10pt]{article}

\title{Response to Reviewers: \\ T-ASL-05872-2016 "Object-based Auditory Scenes Similarity Retrieval and Classification With Wavelet Scattering"}

\usepackage{color}
\newcommand{\vl}[1]{\textcolor{red}{Vincent : #1}}
\newcommand{\ja}[1]{\textcolor{magenta}{Joakim : #1}}
\newcommand{\ml}[1]{\textcolor{blue}{ Mathieu : #1}}

@@

\item \emph{Confusion matrix of the two best methods will be interesting.}

\item \emph{The cross-validation analyses confirmed that the value T = 372 ms for the support of the low-pass filter is optimal when applying late integration by majority voting, but shall it adapted per classes  ?}

\item \emph{A table with the 2016 CASE private results may be added (or replace Tab III).}

\item \emph{The bibliography is huge, it may be reduced by 10 \%.}

\item \emph{Check typos in the references (Museum, Histoire nat...). “befor”}

\item \emph{Bregman shall be cited in the discussion about  binding of acoustic cues.}

\ja{can you spot where we speak oabout binding acoustic cues ?, I can't ;(}

### 2016-12-06 paper/structureScene.tex
improving bib

\IEEEPARstart{T}{he} amount of audio data recorded from our sonic environment has grown considerably over the past decades.
In order to measure the effect of human activity and climate change on animal biodiversity, researchers in the field of ecoacoustics \cite{ECOACOUSTICS2014, krause} have recently undertaken the massive deployment of acoustic sensors throughout the world \cite{warren2006urban, NessSST13, stowell13a, stowell13b}.

In addition, recent work demonstrates the interest of acoustic monitoring for the characterization of human pleasantness in urban areas \cite{lafayPartI, guyot2005urban, ricciardi2015sound} as well as the prediction of annoyance due to traffic \cite{gloaguen}.
Because they bear a strong societal impact and raise many scientific challenges, we believe that these case studies are of considerable interest for the signal processing community.

@@

A closely related, and more mature, field of investigation is the classification of acoustic scenes, where the aim is to predict labels by processing audio data.
While narrower in its range of applications, it has the advantage of being rooted in cognitive psychology of categorization \cite{dubois2006cognitive, maffiolo_caracterisation_1999, guastavino_ideal_2006} and has received the attention of the data mining community for some time, resulting in the availability of well-designed datasets.

@@

This statement has some support in auditory psychology as well as sound synthesis based on summary statistics \cite{mcdermott2013summary}. Indeed, studies in cognitive psychology investigating urban sound environment quality pointed out that global sound level (perceived or measured) is not sufficient to fully characterize an acoustic scene \cite{guyot2005urban,kang2006urban}. Rather, it seems that cognitive processes such as sound environment quality perception \cite{dubois2006cognitive} or loudness judgment \cite{kuwano_memory_2003} rely upon higher-level cognitive attributes such as the identities of the sound sources which compose the scene. It has been showed that, if available, the complete description of the scene in terms of event occurrences is powerful enough to reliably predict high-level cognitive classes, \eg the presence of birds are very likely to be heard in parks in urban areas and so are strong pleasantness indicators \cite{lafayPartI}. Consequently, research in sound perception is now strongly focused the contribution of specific sound sources in the assessment of a sound environment \cite{ricciardi2015sound,lavandier2006contribution}. Although the complete set of events occuring within a given auditory stream may not be discernable, even to human expects, research has shown that a small set of events, so called markers, suffice to reliably predict many high-level attributes.

@@

\begin{table}
\begin{center}
\caption{Algorithms evaluated on the DCASE 2013 private dataset of acoustic scene classification. RQA stands for recurrence quantification analysis and ILD for inter-aural differences. Algorithms above the horizontal line participated to the DCASE challenge. Others used the datasets afterward and the last considered only the public dataset ($^*$).  \label{tab:dcase}}
\begin{tabular}{lcl}
& Acc. \%  &  \multicolumn{1}{c}{Design}  \\
\hline
\cite{olivetti2013wonder} OE & 17 & compression distance, random forests \\
\cite{elizalde2013vector} ELF & 55 & i-vector, LDA \\
\cite{krijnders2013tone} KH & 55 & cochleogram, SVMs \\
\cite{patil2013multiresolution} PE & 58 & 2D Gabor filters, SVMs \\
\cite{lee2013acoustic} NHL & 60 & unsupervised learning over mel spectra, SVMs \\
\cite{nogueira2013sound} NR1 & 60 & MFCCs and ILD features, SVMs \\
\cite{chum2013ieee} CHR & 65 & sparsity features, HMMs  \\
\cite{geiger2013large} GSR & 69 & mel spectra and MFCCs, SVMs \\
\cite{rakotomamonjy2015histogram} RG & 69 & histogram of gradient (HOG), SVMs \\
\cite{li2013auditory} LTT & 72 & MFCCs, tree baggers \\
\cite{roma2013recurrence} RNH & 76 & RQA features stacked with MFCCs, SVMs \\
\hline
\cite{phan2016label} & 84/87 & label tree embedding of Gammatone, SVMs \\
\cite{7362846} & 85$^*$ & amplitude modulated spectra, LDA \\
\end{tabular}
\end{center}
\end{table}

@@

Those outcomes shall be studied further in future work by considering larger databases and more diverse applications, such as pleasantness prediction \cite{lafaySoundscapePilot, lafayPartI} as well as emerging tasks in ecoacoustics.

>>>>

\IEEEPARstart{T}{he} amount of audio data recorded from our sonic environment has grown considerably over the past decades.
In order to measure the effect of human activity and climate change on animal biodiversity, researchers in the field of ecoacoustics \cite{krause} have recently undertaken the massive deployment of acoustic sensors throughout the world \cite{warren2006urban, NessSST13, stowell13a, stowell13b}.

In addition, recent work demonstrates the interest of acoustic monitoring for the characterization of human pleasantness in urban areas \cite{guyot2005urban, ricciardi2015sound} as well as the prediction of annoyance due to traffic \cite{gloaguen}.
Because they bear a strong societal impact and raise many scientific challenges, we believe that these case studies are of considerable interest for the signal processing community.

@@

A closely related, and more mature, field of investigation is the classification of acoustic scenes, where the aim is to predict labels by processing audio data.
While narrower in its range of applications, it has the advantage of being rooted in cognitive psychology of categorization \cite{dubois2006cognitive, guastavino_ideal_2006} and has received the attention of the data mining community for some time, resulting in the availability of well-designed datasets.

@@

This statement has some support in auditory psychology as well as sound synthesis based on summary statistics \cite{mcdermott2013summary}. Indeed, studies in cognitive psychology investigating urban sound environment quality pointed out that global sound level (perceived or measured) is not sufficient to fully characterize an acoustic scene \cite{guyot2005urban,kang2006urban}. Rather, it seems that cognitive processes such as sound environment quality perception \cite{dubois2006cognitive} or loudness judgment \cite{kuwano_memory_2003} rely upon higher-level cognitive attributes such as the identities of the sound sources which compose the scene. It has been showed that, if available, the complete description of the scene in terms of event occurrences is powerful enough to reliably predict high-level cognitive classes, \eg the presence of birds are very likely to be heard in parks in urban areas and so are strong pleasantness indicators. Consequently, research in sound perception is now strongly focused on the contribution of specific sound sources in the assessment of a sound environment \cite{ricciardi2015sound,lavandier2006contribution}. Although the complete set of events occurring within a given auditory stream may not be discernable, even to human expects, research has shown that a small set of events, so called markers, suffice to reliably predict many high-level attributes.

@@

\begin{table}
\begin{center}
\caption{Algorithms evaluated on the DCASE 2013 private dataset of acoustic scene classification. RQA stands for recurrence quantification analysis and ILD for inter-aural differences. Algorithms above the horizontal line participated to the DCASE challenge. Others used the datasets afterward and the last considered only the public dataset ($^*$).  \label{tab:dcase}}
\begin{tabular}{lcl}
& Acc. \%  &  \multicolumn{1}{c}{Design}  \\
\hline
\cite{olivetti2013wonder} OE & 17 & compression distance, random forests \\
\cite{elizalde2013vector} ELF & 55 & i-vector, LDA \\
\cite{krijnders2013tone} KH & 55 & cochleogram, SVMs \\
\cite{patil2013multiresolution} PE & 58 & 2D Gabor filters, SVMs \\
\cite{lee2013acoustic} NHL & 60 & unsupervised learning over mel spectra, SVMs \\
\cite{nogueira2013sound} NR1 & 60 & MFCCs and ILD features, SVMs \\
\cite{chum2013ieee} CHR & 65 & sparsity features, HMMs  \\
\cite{geiger2013large} GSR & 69 & mel spectra and MFCCs, SVMs \\
\cite{rakotomamonjy2015histogram} RG & 69 & histogram of gradient (HOG), SVMs \\
\cite{li2013auditory} LTT & 72 & MFCCs, tree baggers \\
\cite{roma2013} RNH & 76 & RQA features stacked with MFCCs, SVMs \\
\hline
\cite{phan2016label} & 84/87 & label tree embedding of Gammatone, SVMs \\
\cite{7362846} & 85$^*$ & amplitude modulated spectra, LDA \\
\end{tabular}
\end{center}
\end{table}

@@

Those outcomes shall be studied further in future work by considering larger databases and more diverse applications, such as pleasantness prediction \cite{lafaySoundscapePilot} as well as emerging tasks in ecoacoustics.
